%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
	{System Engineer \& Software Engineer} % Job title
    {Fujitsu Network Solutions Ltd. } % Organization
    {Yokohama, Kanagawa, Japan} % Location
    {Apr. 2017 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developer for DLIST Manager by Utilizing A10 Networks Thunder Series RESTfull API with Azure Serverless Function App to control domain list}
        \item {Maintaining Fujitsu Network Solutions Cloud 2 deployed using VMWARE Esxi 5.0 }
        \item {Main team to control sales release for A10 Thunder Series and managing all main process to sell  A10 Networks Thunder Series as Fujitsu Network Solutions is partner with A10 Networks(from Design to Operation)}
        \item{Responsible for design, plan, develop for A10 Automation Program for testing A10 Networks Thunder Series using RESTful API with Python}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
	{Founder \& Full-Stack Developer } % Job title
	{Alka Corp (Start-up company)} % Organization
    {Kuala Lumpur, Malaysia} % Location
    {June. 2017 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Managing and planning Alka Corp project }
        \item {Developing webiste for Premise reservation project with MEAN stack}
        \item {Designing and developing the image for Alka Corp }
      \end{cvitems}
    }
	
%---------------------------------------------------------
  \cventry
	{Research Assistant \& Programmer \& Graduate Student} % Job title
	{Nikon Corp. \& Keio University (Kuroda Lab)} % Organization
    {Tokyo, Japan} % Location
    {May. 2014 - Feb. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Managing 3D model dataset that will be used to train image detector}
        \item {Creating application to automate the generation of 3D models human with Blender by using Python}
        \item {Testing and improving algorithms for image detection technology that will be used in the next version of NIKON camera}
        \item {Testing algorithms in MATLAB environment with integration with C++ to implemeted the tested detector inside the hardware processing unit}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Interns} % Job title
    {JFE Engineering} % Organization
    {Yokohama, Japan} % Location
    {Aug. 2015 - Sep. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Learn about incinerator in Japan and learned the mechanism and technology of the incinerator}
        \item {Attending Project Management course on how to handle big scale project}
        \item {Working as a incinerator power plant engineer by solving any problem during workday by implementing scheduling technique }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Service Staff} % Job title
    {Tokyu Corp.} % Organization
    {Yokohama, Japan} % Location
    {Apr. 2014 - Mar. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintaining cleanliness and safety for train passenger during rush hour in Ookayama Station}
        \item {Improved confidence skill and time management skill as train need to be on time }
      \end{cvitems}
    }

  \cventry
    {Staff} % Job title
    {Meguro-Ku Kuyakusho} % Organization
    {Meguro, Japan} % Location
    {Aug. 2013 - Sep. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Part time worker as garbage collector around Meguro-Ku}
        \item {Improved alot of Japanese skills by interacting with other Japanese workers for the first time}
      \end{cvitems}
    }
\end{cventries}
